### 2013-11-20 regressionModelling.Rmd
Intermediate commit.. Adding perceived gini and 2006 data

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

>>>>

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.social ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarSocOutputNOCI, results='asis'}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod",
                     "Perceived Gini")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12,
             bisoc.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.individual ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarIndOuputNOCI, results='asis'}

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
